Jane, John … Leslie? A Historical Method for Algorithmic Gender Prediction

### 2015-08-21 article.Rmd
Typos

The Kantrowitz corpus provides the list of names.^[The examples below is drawn from our Gender package which implements the Kantrowitz dataset for sake of comparsion, though its use is not recommended for actual research. The Gender package combines the Kantrowitz corpus's two lists into a single list, identifying names that are ambiguous because they appear on both lists as `"either"`.]

@@

Nevertheless, the methodology that have described here does take advantage of the datasets available to historians. The predictions it provides are not intended to be taken as the entirety of what historians can say about gender in the past. But they provide the ability to uncover data about gender where it was previously unknown, thus providing further grist to the mill of more traditional methods. Furthermore, the gender package is entirely open-source, and we have provided detailed documentation for its code and underlying data so that researchers who wish to build upon it can modify the package accordingly. By building as much flexibility and transparency into the method as possible, we hope that others can continue to make just these kinds of improvements.

>>>>

The Kantrowitz corpus provides the list of names.^[The examples below is drawn from our Gender package which implements the Kantrowitz dataset for sake of comparison, though its use is not recommended for actual research. The Gender package combines the Kantrowitz corpus's two lists into a single list, identifying names that are ambiguous because they appear on both lists as `"either"`.]

@@

Nevertheless, the methodology that we have described here does take advantage of the datasets available to historians. The predictions it provides are not intended to be taken as the entirety of what historians can say about gender in the past. But they provide the ability to uncover data about gender where it was previously unknown, thus providing further grist to the mill of more traditional methods. Furthermore, the gender package is entirely open-source, and we have provided detailed documentation for its code and underlying data so that researchers who wish to build upon it can modify the package accordingly. By building as much flexibility and transparency into the method as possible, we hope that others can continue to make just these kinds of improvements.
